|

### 2024-10-26 docs/presentation.qmd
presentation changes for brown bag
Pre SSRN

---
title: "Accountants' Attitudes Towards Open Science"
subtitle: "" # we use this for the venue
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

@@

>>>>

---
title: |
  | How does the Accounting Research Community 
  | Think About Open Science?
subtitle: "" # we use this for the venue
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

@@

## To Compare: Policy Effect for Management Science

\begin{center}
\includegraphics[width =0.7\textwidth]{"materials/fisar_et_al_2023_policy.jpeg"} \\
Fišar et al. (2023, Management Science)
\end{center}
